---
title: "Israeli Peripherality Data"
author: "Anna Weiner"
date: "2024-02-25"
output: 
  pdf_document:
    includes:
      in_header: header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  eval = TRUE, 
  fig.align='center',
  message=FALSE, 
  warning=FALSE
)

knitr::knit_hooks$set(
  inline = function(x) {
    if(!is.numeric(x)){x}else{
      prettyNum(round(x, 2), big.mark = ',')
    }
  }
)
  
library(tidyverse)
library(knitr)
library(readxl)

load("/Users/annaweiner/Downloads/Programming/Codebook/Israel_Peripherality_Data.RData")

cbfactor = function(.data, x){
    x = enquo(x)
    count(.data, !!x) |>
      mutate(
        values = as.numeric(!!x),
        labels = as_factor(!!x),
        freq = n,
        perc = n / sum(n) * 100,
        .keep = 'unused'
      ) |>
      knitr::kable(digits = 1L)
}

numfunction = function(.data, x){
    x = enquo(x)
    .data |>
     summarize(
      Min = min(!!x, na.rm = T),
      Mean = mean(!!x, na.rm = T),
      Median = median(!!x, na.rm = T),
      Max = max(!!x, na.rm = T),
      NAs = sum(is.na(!!x))
    ) |>
    knitr::kable(digits = 1L)   
}    
```

## Overview
This code book contains information on peripherality data from Israel in 2020. The data was procured from Israel's Central Bureau of Statistics (CBS) and was compiled by Natalia Tsibel on December 26, 2022. More information on data collection methods and the compilation process can be found by emailing the CBS at info@cbs.gov.il

## Methodology
Demographic data was collected from Israel's localities, who report various demographic data to the central government annually. 

Accessibility and proximity values are based on data received from regional councils, then calculated as a mean value for each localities within the regional council and weighted by population size.

Peripherality index values are calculated as the weighted sum of the standardized values of the potential accessibility index. 2/3 of the weight is the Accessibility Value, and 1/3 of the weight is proximity to the boundary of the Tel Aviv District.

All missing data is marked as "NA".

## Code Book

Variable name: local_authority  
Variable type: character   
Description: Name of local authority, refers to the same metric as "region" or "regional authority."

Variable name: locality   
Variable type: character     
Description: Name of locality.   

Variable name: locality_code   
Variable type: numeric   
Description: Government-assigned code to each locality.    
```{r}
numfunction(codebook_clean, locality_code)
```

Variable name: municipal_status   
Variable type: numeric   
Description: Central-government designated number for regional jurisdiction.    
```{r}
numfunction(codebook_clean, municipal_status)
```

Variable name: population_2020   
Variable type: numeric   
Description: Number of residents per locality in 2020.   
```{r}
numfunction(codebook_clean, population_2020)
```

Variable name: centrality   
Variable type: factor   
Description: Ranks distance from Tel Aviv. "Central" refers to localities within 75 kilometers of Tel Aviv, "Suburban" refers to localities 75-150 kilometers from Tel Aviv, and "Peripheral" refers to localities over 150 kilometers from Tel Aviv.       
```{r}
cbfactor(codebook_clean, centrality)
```

Variable name: km_from_tlv   
Variable type: numeric   
Description: The number of kilometers a region is from Tel Aviv.     
```{r}
numfunction(codebook_clean, km_from_tlv)
```

Variable name: prox_tlv_value   
Variable type: numeric   
Description: Standardized score (z-score) of a locality's region's distance from Tel Aviv.  
```{r}
numfunction(codebook_clean, prox_tlv_value)
```

Variable name: prox_tlv_rank   
Variable type: numeric   
Description: The variable `prox_tlv_rank` ranked, scale 1 to 1213.     
```{r}
numfunction(codebook_clean, prox_tlv_rank)
```

Variable name: accessibility_value   
Variable type: numeric   
Description: A mean value for each locality within each regional council and weighted by population size. Determines accessibility to transportation infrastructure to Israel's center.  
```{r}
numfunction(codebook_clean, accessibility_value)
```

Variable name: accessibility_rank   
Variable type: numeric   
Description: The variable `accessibility_value` ranked, scale 1 to 1213.    
```{r}
numfunction(codebook_clean, accessibility_rank)
```

Variable name: peri_index_2020_value  
Variable type: numeric   
Description: A mean value for each locality within each regional council and weighted by population size, determines score on Israel's peripherality index for 2020.    
```{r}
numfunction(codebook_clean, peri_index_2020_value)
```

Variable name: peri_index_2020_rank   
Variable type: numeric  
Description: The variable `peri_index_2020_rank` ranked, scale 1 to 1213.   
```{r}
numfunction(codebook_clean, peri_index_2020_rank)
```